Supplementary Material for _A Guide to Pre-processing High-Frequency Animal Tracking Data_

### 2021-09-13 supplement/06_bat_data.Rmd
edits for fig 1

```{r plot_heatmap}
fig_heatmap <-
  ggplot(data_heatmap) +
  geom_tile(
    aes(
      xround, yround,
      fill = N
    ),
    colour = "grey",
    size = 0.1,
    show.legend = F
  ) +
  scale_fill_viridis_c(
    option = "C",
    direction = 1,
    trans = "log10"
  ) +
  ggthemes::theme_few() +
  theme(
    axis.text = element_blank(),
    axis.title = element_blank()
  ) +
  coord_sf(crs = 2039)

@@

# make figure
fig_lags <-
  ggplot(data_for_intervals) +
  geom_histogram(
    aes(
      x = lag / 8,
      fill = (lag / 8 > 3)
    ),
    position = position_identity(),
    bins = 15,
    # fill = "grey",
    col = "black",
    show.legend = F
  ) +
  geom_vline(
    xintercept = 1,
    col = "red"
  ) +
  scale_x_log10(
    labels = function(x) {
      sprintf("%ix", x)
    },
    breaks = c(1, 3, 10, 100, 1000)
  ) +
  scale_y_sqrt() +
  scale_fill_viridis_d(
    option = "H",
    begin = 0.1,
    end = 0.8
  ) +
  ggthemes::theme_few() +
  theme(
    axis.text.y = element_blank(),
    axis.text.x = element_text(
      face = "bold",
      size = 16
    ),
    axis.title.y = element_blank(),
    axis.title.x = element_text(
      face = "bold",
      size = 16
    )
  ) +
  labs(x = "Sampling interval")

@@

```{r localisation_error, echo=FALSE}
fig_error_histogram <-
  ggplot(data) +
  geom_histogram(
    aes(
      x = sqrt(VARX),
      fill = (sqrt(VARX) > 100)
    ),
    bins = 15,
    # fill = "grey",
    col = "black",
    show.legend = F
  ) +
  scale_fill_viridis_d(
    option = "H",
    begin = 0.1,
    end = 0.8
  ) +
  scale_x_log10(
    labels = function(x) {
      sprintf("%2.fm", x)
    }
  ) +
  scale_y_sqrt() +
  coord_cartesian(
    xlim = c(0.5, 5e3)
  ) +
  ggthemes::theme_few() +
  theme(
    axis.text.y = element_blank(),
    axis.text.x = element_text(
      face = "bold",
      size = 16
    ),
    axis.title.y = element_blank(),
    axis.title.x = element_text(
      face = "bold",
      size = 16
    )
  ) +
  labs(x = "Variance X")

@@

```{r echo=FALSE}
# plot bat data to examine for errors
fig_bat_raw <-
  ggplot(data) +
  geom_path(aes(X, Y,
    group = TAG,
    colour = TAG
  ),
  show.legend = FALSE
  ) +
  scale_colour_brewer(palette = "Dark2") +
  ggspatial::annotation_scale(location = "br") +
  ggthemes::theme_few() +
  theme(
    axis.text = element_blank(),
    axis.title = element_blank()
  ) +
  coord_sf(crs = 2039)
```

@@

```{r echo=FALSE}
# save to figures
ggsave(fig_bat_smooth,
  filename = "supplement/figures/fig_bat_smooth.png",
  dpi = 300,
  width = 4, height = 6
)
```

>>>>

```{r plot_heatmap}
fig_heatmap <-
  ggplot(data_heatmap) +
  geom_tile(
    aes(
      xround, yround,
      fill = N
    ),
    size = 0.1,
    show.legend = F
  ) +
  scale_fill_viridis_c(
    option = "A",
    direction = -1,
    trans = "log10"
  ) +
  theme_void() +
  coord_sf(crs = 2039)

@@

# make figure
fig_lags <-
  ggplot(data_for_intervals) +
  geom_histogram(
    aes(
      x = lag / 8,
      fill = (lag / 8 > 3)
    ),
    position = position_identity(),
    bins = 15,
    # fill = "grey",
    # col = "black",
    show.legend = F
  ) +
  scale_x_log10(
    breaks = c(1, 1000),
    labels = c("low", "high")
  ) +
  scale_y_sqrt() +
  scale_fill_viridis_d(
    option = "B",
    begin = 0.4,
    end = 0.8
  ) +
  theme_void() +
  theme(
    axis.text.y = element_blank(),
    axis.text.x = element_text(
      face = "bold",
      size = 16
    ),
    axis.title.y = element_blank(),
    axis.title.x = element_text(
      face = "bold",
      size = 16
    )
  ) +
  labs(x = "Sampling interval")

@@

```{r localisation_error, echo=FALSE}
fig_error_histogram <-
  ggplot(data) +
  geom_histogram(
    aes(
      x = sqrt(VARX),
      fill = (sqrt(VARX) > 100)
    ),
    bins = 15,
    # fill = "grey",
    # col = "black",
    show.legend = F
  ) +
  scale_fill_viridis_d(
    option = "B",
    begin = 0.4,
    end = 0.8
  ) +
  scale_x_log10(
    breaks = c(1, 1000),
    labels = c("low", "high")
  ) +
  scale_y_sqrt() +
  coord_cartesian(
    xlim = c(0.5, 5e3)
  ) +
  theme_void()+
  theme(
    axis.text.y = element_blank(),
    axis.text.x = element_text(
      face = "bold",
      size = 16
    ),
    axis.title.y = element_blank(),
    axis.title.x = element_text(
      face = "bold",
      size = 16
    )
  ) +
  labs(x = "Positioning error")

@@

```{r echo=FALSE}
# plot bat data to examine for errors
fig_bat_raw <-
  ggplot(data) +
  geom_path(aes(X, Y,
    group = TAG,
    colour = TAG
  ),
  show.legend = FALSE
  ) +
  scale_colour_brewer(palette = "Dark2") +
  ggspatial::annotation_scale(location = "br") +
  theme_void()+
  theme(
    axis.text = element_blank(),
    axis.title = element_blank()
  ) +
  coord_sf(crs = 2039)
```

@@

```{r echo=FALSE}
# save to figures
ggsave(fig_bat_smooth,
  filename = "supplement/figures/fig_bat_smooth.png",
  dpi = 300,
  width = 4, height = 6
)

# for fig 1
ggsave(
  fig_bat_smooth + theme_void(),
  filename = "supplement/figures/fig_bat_preproc_f1.png",
  dpi = 300,
  width = 4, height = 6
)
```
